Software Citation Principles

### 2016-02-16 sc-principles/software-citation-principles.tex
tweaks to authors, adding new paragraph in intro

\author{Force11 Software Citation Working Group (Smith Katz Niemeyer eds)}

@@

>>>>

\author{Force11 Software Citation Working Group (Editors: Arfon M. Smith, Daniel S. Katz, Kyle E. Niemeyer)}

@@

The Force11 Software Citation Working Group~\cite{f11scwg} has been studying this,
beginning in ...  with a number of meetings ... and has prepared this document for
presentation at Force2016~\cite{force2016} and further discussion.  We expect that
this discussion may lead to a second, final version of this document, and we also
plan to have a follow-on working group that will work with stakeholders to ensure that
these principles impact the scientific process.
